---
title: "Chocolate"
subtitle: "Kruskal-Wallis Test"
---

```{r, include=FALSE}
# Be sure to use your file menus at the top of R-Studio to:
# "Session -> Set working directory -> To source file location"
# Then play this chunk and the next one to get the data into R.
library(mosaic)
library(car)
library(DT)
library(pander)
library(tidyverse)
# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
choc <- read_csv("../Data/Chocolate.csv") %>% 
  na.omit() %>% mutate(Cocao = parse_number(as.character(Cocao)))


choc$Cocoa <- cut(choc$Cocao, c(41,60,69,79,89,100), labels=c("Medium-Chocolate", "Dark", "Double-Dark", "Extra-Dark", "Super-Dark"),ordered_result = TRUE)
```

```{r, eval=FALSE}
getwd()
View(choc)
```

<!-- ---- -->

<!-- Instructions:

 Use the Chocolate dataset and a Kruskal-Wallis Test(s) to answer an interesting question(s) that you come up with.
 
 About the dataset:
 
  * Company: Name of the company manufacturing the bar.

  * Orig: The specific geo-region of origin for the bar.

  * Review: Date of publication of the review.

  * Cocoa: Cocoa percentage (darkness) of the chocolate bar being reviewed.

  * Location: Manufacturer base country.

  * Rating: Expert rating for the bar.
      5= Elite (Transcending beyond the ordinary limits)
      4= Premium (Superior flavor development, character and style)
      3= Satisfactory(3.0) to praiseworthy(3.75) (well made with special qualities)
      2= Disappointing (Passable but contains at least one significant flaw)
      1= Unpleasant (mostly unpalatable)

   * Type: The variety (breed) of cocoa bean used, if provided.
   
   * BroadOrig: The broad geo-region of origin for the bean.

Note this dataset and description come from: © 2018 Kaggle Inc for further details visit:

[Kaggle.com](https://www.kaggle.com/rtatman/chocolate-bar-ratings/data)


If you want to give your critiquers some ideas about what you have questions on and would like help with, place those details here.-->
<!-- **Comments to Critiquers:**  -->



<!--End your comments to your critiquers before this line.-->

<!-- ---- -->

<!--Begin writing your Analysis after this point.-->

## Background 

There are many different Chocolate bars in the dataset. I will be comparing how percent cocoa and rating is compared.  

In this data the each experimental unit is assigned to exactly one factor-level combination. Another way to say this is “one measurement per individual” (no repeated measures) and “equal numbers of individuals per group”.

This test is done using Kruskal-Wallis and One-Way ANOVA. What percent Cocoa has the greatest rating? 


$$
  H_0: \mu_\text{Rating} = \mu_\text{Cocao} = \mu
$$

$$
  H_a: \mu_\text{Rating} \neq \mu_\text{Cocao}
$$


## Data Analysis {.tabset .tabset-fade}

### Basic Statistics

```{r}
pander(favstats(Rating ~ Cocoa, data = choc)[,-10])
```

### Kruskal-Wallis Test

```{r}
mykruskal <- kruskal.test(Rating ~ Cocoa, data=choc)
pander(mykruskal)
```

```{r}
boxplot(Rating ~ Cocoa, data=choc, type=c("p","a"), col='grey', xlab="Percent of Cocoa", ylab="Rating of Chocolate", main="Rating vs Percent Cocoa")
```

### ANOVA Test

```{r}
myaov <- aov(Rating ~ Cocoa, data=choc)
pander(myaov)
```

```{r message=FALSE, warning=FALSE}
par(mfrow = c(1,2))
plot(myaov, which=1:2)
```

### The Data

```{r, out.width=300}
pander(choc, split.tables = Inf)
```

## Interpretation

In this analysis I compared the percent of cocoa to rating of chocolate. 

Rating is on a 1 to 5 scale. 

1. Unpleasant
2. Disappointing
3. Satisfactory
4. Premium 
5. Elite 

Percent Cocoa is broken into 

* Medium-Chocolate
* Dark
* Double-Dark
* Extra-Dark
* Super-Dark

Over all the Double Dark is the highest rating. We learn from the Kruskal-Wallis that the P-value is 1.462e-18 with 4 degrees of freedom. The P-value represents the probability of H, assuming the null hypothesis is true. The P-value is super small so we have insuffent evidence to conclude the distribution groups. 



<!-- ```{r} -->
<!-- hist(choc$Rating, breaks=15, col='sandybrown', xlab="Rating of Chocolate", main="Chocolate Rating") -->
<!-- ``` -->