---
title: "Spotify"
subtitle: "Consulting Project"
date: "Week 9"
editor_options: 
  chunk_output_type: console
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r include=FALSE}
library(mosaic)
library(car)
library(DT)
library(pander)
library(tidyverse)

spotify <- read_csv("https://raw.githubusercontent.com/byui-cse/cse450-course/master/data/spotify/data.csv") %>% 
  na.omit() %>% 
  select(-release_date, -id, -name, - artists) %>% 
  filter(year >= 2015)

pandary <- function(x){pander(summary(x))}
```

```{r eval=FALSE, include=FALSE}
View(spotify)
colnames(spotify)
```

## Background

My friend [Freddy Velazquez](https://www.instagram.com/freddyv98/) is in need of help figuring out what makes music more popular. [Canillas (Freddy)](https://open.spotify.com/artist/40rHTqqZNlzw3TrcVXlSUI) has 26 monthly listeners, and is trying to get more listeners. This would help since his new album comes out soon. I will be using a Linear Regression model to figure out what makes music popular. The [spotify data](https://raw.githubusercontent.com/byui-cse/cse450-course/master/data/spotify/data.csv) I am using is from 2015 to 2020.   

<br /> <br /> <hr />

## Data Analytics {.tabset .tabset-fade}

### Basic Stats 

#### Summary of Popularity

```{r}
pandary(spotify$popularity)
```

#### Fav Stats of Popularity based on Year

```{r}
pander(favstats(popularity ~ year, data = spotify)[,-10])
```

<br /> <br /> <hr />

### Linear Regression {.tabset .tabset-pills}

```{r}
simple <- function(x){
  
  # Preform Regression
  
  mylm <- lm(popularity ~ x, data = spotify)
  
  # Diagnostic
  
  par(mfrow=c(1,3))
  plot(mylm, which=1:2)
  plot(mylm$residuals)
  
  # Create Plot
  
  myplot <- ggplot(spotify, aes(y = popularity, x = x)) +
    geom_point(color = "red") +
    geom_smooth(method = "lm", se=FALSE, color = "black") +
    theme_bw()
  
  # Create List and Return List
  
  mylist <- list("lm" = mylm, "plot" = myplot)
  return(mylist)
}
```

#### Danceability

```{r}
lm_danceability <- simple(spotify$danceability)
pandary(lm_danceability$lm)
lm_danceability$plot
```

<br /> <br /> <hr />

#### Duration

```{r}
lm_duration <- simple(spotify$duration_ms)
pandary(lm_duration$lm)
lm_duration$plot
```

<br /> <br /> <hr />

#### Energy

```{r}
lm_energy <- simple(spotify$energy)
pandary(lm_energy$lm)
lm_energy$plot
```

<br /> <br /> <hr />

#### Liveness

```{r}
lm_liveness <- simple(spotify$liveness)
pandary(lm_liveness$lm)
lm_liveness$plot
```

<br /> <br /> <hr />

#### Loudness

```{r}
lm_loudness <- simple(spotify$loudness)
pandary(lm_loudness$lm)
lm_loudness$plot
```

<br /> <br /> <hr />

#### Tempo

```{r}
lm_tempo <- simple(spotify$tempo)
pandary(lm_tempo$lm)
lm_tempo$plot
```

<br /> <br /> <hr />

#### Year

```{r}
lm_year <- simple(spotify$year)
pandary(lm_year$lm)
lm_year$plot
```

<br /> <br /> <hr />

## Interpretation

First I would like to mention that as years go on new songs increase in popularity, which is good for you. Next lets see what each regression tells us. 

* Danceability - Increasing popularity with increasing Danceability - Slope = 6.623
* Duration - Decreasing popularity with increasing duration - Slope = -2.066e-05
* Energy -  Decreasing popularity with increasing energy - Slope = -1.572
* Liveness - Decreasing popularity with increasing liveness - Slope = -2.534
* Loudness - Increasing popularity with increasing loudness - Slope = 0.04487
* Tempo - Decreasing popularity with increasing tempo - Slope = -1.17e-06
* Year - Increasing popularity with increasing year - Slope = 1.362

So basically it is danceable and loud then it would have a high popularity.

Freddy your music fits both being danceable and loud so so as lonas it's not super long that your music would be popular. 