---
title: "High School Seniors"
subtitle: "t Test"
---

```{r load, message=FALSE, warning=FALSE}
library(tidyverse)
library(DT)
library(pander)
library(mosaic)
library(car)

setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

dat <- read_csv("../Data/HighSchoolSeniors.csv") %>% na.omit()
#Remember: select "Session, Set Working Directory, To Source File Location", and then play this R-chunk into your console to read the HSS data into R. 

HSS <- dat %>% select(Gender, Ageyears, Video_Games_Hours, Social_Websites_Hours, Texting_Messaging_Hours, Computer_Use_Hours, Watching_TV_Hours)
```

```{r View, eval=FALSE, include=FALSE}
View(HSS)
names(HSS)
```


## Instructions

1. Use the HSS dataset in R to come up with a question that can be answered with a t Test. 
  + Here is a link to the survey given to the students that participated in the [study](https://ww2.amstat.org/censusatschool/pdfs/C@SQuestionnaire.pdf):
  + (Use the link to learn about what each column of data in the data set represents.)

2. Establish why your question is interesting and rephrase the question using a statistical "null" and "alternative" hypothesis. 
  + (Hint, see the "Math 325 Notebook -> R Help -> R-Markdown Hints" page of your textbook for instructions on how to write mathematical hypotheses.)

3. Clearly answer your question using statistics. Be sure to compute a p-value and provide supporting numerical and graphical summaries. 
  + Note: you can create "groups" from the data in many ways. 

## Questions and Hypotheses

How does electronic use time relate to gender? 
Do males spend more time on electronics? 

$$
  H_0: \mu_\text{electronic use} - \mu_\text{gender} = 0
$$

$$
  H_a: \mu_\text{electronic use} - \mu_\text{gender} \neq 0
$$

## Data Analysis

Brief Glimpse (Names) of the Data

```{r base}
names(HSS)
```

```{r wrangling}
newHSS <- HSS %>% 
  mutate(Electronic_Use = Video_Games_Hours + Social_Websites_Hours + Texting_Messaging_Hours + Computer_Use_Hours + Watching_TV_Hours) %>% 
  select(- Video_Games_Hours, - Social_Websites_Hours, - Texting_Messaging_Hours, - Computer_Use_Hours,  - Watching_TV_Hours) %>% 
  filter(Electronic_Use <= 160)
```

```{r numerical}
datatable(newHSS, options=list(lengthMenu = c(5,10,50)), extensions="Responsive")
```

## Graphical Summaries

Where do the outliers lay? What gender has more outliers? Which gender's data stays closer to mean? 

```{r graphical1}
ggplot(data = newHSS) + 
  geom_boxplot(aes(x = Gender, y = Electronic_Use)) +
  theme_bw()
```




What gender has a higher total electronic use time per week? 

```{r graphical2}
ggplot(data = newHSS) + 
  geom_col(aes(x = Gender, y = Electronic_Use)) +
  theme_bw()
```




## Interpretation

Based on the graphical summaries my hypothesis was wrong. Yet we aren't for sure on what the true conclusions. We can try t-tests which will give a closer and more exact conclusion. 

```{r tests}
t.test(Electronic_Use ~ Gender, data = newHSS, mu = 0, alternative = "two.sided", conf.level = 0.95)
```

```{r qqplot}
qqPlot(Electronic_Use ~ Gender, data = newHSS)
```

