---
title: "Chi Squared Test"
editor_options: 
  chunk_output_type: console
---


<!-- Directions

Come up with a chi squared test analysis of your own creation. 

* Write the Background and clearly state your question. Then collect data and perform the chi-squared test analysis in order to answer your question. Use the proper order of first, ask the question, then second, figure out the answer.

* You can use data from 
    - An R data set
    - the internet (like weather data, Facebook data, or sports data) 
    - your own experiment 
    - your own observational study
* However,     
    - Do not violate the "Human Subjects Rules" of the university: http://www.byui.edu/executive-strategy-and-planning/institutional-research/research-and-assessments/research-and-surveys

* You need a sample size large enough to meet the requirements of the chi squared test. Unfortunately, the sample size is completely dependent on the situation you select. A good rule of thumb is 10 observations per "combination-group" in your data.

-->

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r, include=FALSE}
library(mosaic)
library(car)
library(DT)
library(pander)
library(tidyverse)
library(data.table)

pandary <- function(x){pander(summary(x))}

pander5 <- function(x){pander(x>5)}
```

```{r}
# Use this R-Chunk to import all your datasets!
Guns <- read_csv("https://github.com/kctolli/MATH335/raw/master/Case_Studies/Case_Study_04/analysis/full_data.csv") %>% 
  select(-X1) %>% na.omit() %>% 
  filter(!is.na(intent)) %>% filter(!is.na(age)) %>% 
  select(intent, age, race, education, sex)
```

```{r, eval = FALSE}
View(Guns)
```

## Background

The world is a dangerous place. During 2015 and 2016 there was a lot of discussion in the news about police shootings. FiveThirtyEight reported on gun deaths in 2016. As leaders in data journalism, they have posted a clean version of this data in their [GitHub](https://github.com/fivethirtyeight/guns-data) repo called full_data.csv for us to use. The data of the gun deaths was recorded over the coarse of two years (2012-2014).

## Hypotheses & Data Analysis {.tabset .tabset-fade}

### Is intent associated with education regardless of race? 

$$
  H_{01}:\ \text{Intent and education are not associated.}
$$

$$
  H_{a1}:\ \text{Intent and education are associated.}
$$


```{r}
# Test H_{01}:
gun1 <- table(setDT(Guns %>% select(intent, education)))
chi.gun1 <- chisq.test(gun1); chi.gun1
```

```{r}
pander5(chi.gun1$expected)
```

All expected counts are greater than 5, so the requirements are met. 

```{r}
pander(chi.gun1$residuals)
```

The residuals allow us to visualize how the points follow the test. The values show how far off the data is from the expected values. 

```{r}
barplot(gun1, beside=TRUE, legend.text=TRUE, xlab="Education", main="Education vs Intent")
```

<br />
<hr />

### Is intent associated with race?

$$
  H_{02}:\ \text{Intent and race are not associated.}
$$

$$
  H_{a2}:\ \text{Intent and race are associated.}
$$

```{r}
# Test H_{02}:
gun2 <- table(setDT(Guns %>% select(race, intent)))
chi.gun2 <- chisq.test(gun2); chi.gun2
```

```{r}
pander5(chi.gun2$expected)
```

All expected counts are greater than 5, so the requirements are met. 

```{r}
pander(chi.gun2$residuals)
```

The residuals allow us to visualize how the points follow the test. The values show how far off the data is from the expected values. 

```{r}
barplot(gun2, beside=TRUE, legend.text=TRUE, xlab="Intent", main="Intent vs Race")
```

<br />
<hr />

### Is race associated with education? 

$$
  H_{03}:\ \text{Education and race are not associated.}
$$

$$
  H_{a3}:\ \text{Education and race are associated.}
$$

```{r}
# Test H_{03}:
gun3 <- table(setDT(Guns %>% select(race, education)))
chi.gun3 <- chisq.test(gun3); chi.gun3
```

```{r}
pander5(chi.gun3$expected)
```

All expected counts are greater than 5, so the requirements are met. 

```{r}
pander(chi.gun3$residuals)
```

The residuals allow us to visualize how the points follow the test. The values show how far off the data is from the expected values.  

```{r}
barplot(gun3, beside=TRUE, legend.text=TRUE, xlab="Education", main="Education vs Race")
```

<br />
<hr />

## Interpretation

With each of the of the tests we learn what data is like for the each of the data. For the 3 tests the p-value is the same at < 2.2e-16. Each of the tests did pass the greater than 5 test (If this failed, it will still be appropriate as long as all expected counts are at least 1 and the average expected count is at least 5).