---
title: "Called to Serve"
subtitle: "Simple Logistic Regression"
week: "Week 10"
---

<!-- Find some data of interest to you that can be analyzed with a logistic regression. Complete your Logistic Regression Analysis using this file. 

Hint, run the command 

> data() 

in your Console to see available datasets in R that you could use for this Analysis. You are also welcome to collect data yourself, or find other available datasets online for this Analysis. Just be careful to not use anyone else's "analysis" for this Analysis. Also, no conducting surveys unless you have IRB approval to do so.
Excel Command: =IF(B#="yes", 1, 0)

-->


```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r, include=FALSE}
library(mosaic)
library(ResourceSelection) 
library(pander)
library(tidyverse)
library(DT) 

mission <- read_csv("https://github.com/kctolli/MATH325/raw/master/Data/mission.csv") %>% 
  na.omit() %>% 
  mutate(Mission = if_else(Mission == "yes", 1, 0))

pandary <- function(x){pander(summary(x))}
```

```{r, eval=FALSE, echo=FALSE}
View(mission)
```

## Background

What is the probability of people at certain ages served a mission? Is it an increase or decrease and you get older? 

There are a few steps to answer this question. 

1. Survey people - get age and if they served a mission
2. Collect and wrangle data
3. Use Logistic Regression model to answer the questions
4. Interpret data

## Data Analysis {.tabset .tabset-fade}

### Basic Statistics

```{r}
pander(favstats(Age ~ Mission, data = mission)[,-10])
```

### Logistical Regression

```{r}
mission_glm <- glm(Mission ~ Age, data = mission, family = binomial)
pandary(mission_glm)
```

```{r}
ggplot(mission, aes(Age,Mission)) +
  geom_point(color = "black") +
  geom_smooth(method = glm,
              method.args = list(family = binomial), 
              se = FALSE) +
  theme_bw()
```

```{r}
hoslem.test(mission_glm$y, mission_glm$fitted, g=10)
```

## Interpretation

From the regression we learn that as you get older the odds you served a mission increase by 0.9688. There are a few interesting insights we learn from the data and regression. With COVID-19 sending missionaries home can cause 19 year olds to be returned missionaries. We can see the probabilities of each age using the `predict` function in R.  

```{r}
pander(predict(mission_glm, data.frame(Age = c(18, 19, 20, 21, 22, 23, 24, 25)), type = "response"))
```