---
title: "Rent"
subtitle: "Week 1 Analysis"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
    toc: true
    toc_float: true
---

```{r, include=FALSE}
library(mosaic)
library(pander)
library(tidyverse)
library(DT) 
library(knitr)
Rent <- read_csv("../Data/Rent.csv") %>% na.omit() %>% 
  mutate(MilesToCampus = as.numeric(round(MilesToCampus, digits = 3))) %>% 
  mutate(Price = as.numeric(round(Price, digits = 0)))
```

<br />

## Background

Here is a data table showing the available approved housing apartment options at BYU-Idaho for single students. There are 122 entries comprising 57 female and 65 male apartment options.

```{r, warning=FALSE}
# Code to get you started. 
# View(...) works great in the Console, but datatable(...) must be
# used instead within an R-chunk.
datatable(Rent, options=list(lengthMenu = c(3,10,30)), extensions="Responsive")
```


## Graphic

<!-- Present an interesting graphic using the Rent data set. Do not create the same graphics that are shown in the [Good Example Analysis](./Analyses/StudentHousing.html), but you can certainly use those graphics as a guide to inspire you on what to do yourself. -->

The plot below shows the distribution of distance to campus and cost per semester. 

```{r graphical, warning=FALSE}
# Use this R-chunk to...
# ...Create an interesting graphic using the Rent data set.

ggplot(data = Rent, aes(x = MilesToCampus, y = Price)) +
  geom_point() +
  facet_wrap(~Gender) + 
  theme_bw() +
  labs(x = "Distance to Campus (miles)", y = "Entry-level Cost for Single Housing per Semester")
```


<!-- Write a few statements here that explain your graphic and what it shows. -->

...delete this and type here...

```{r wrangle, warning=FALSE}
# Use this R-chunk to ...
# ...Wrangle, manipulate, and clean the data set.
dat1 <- Rent %>% 
  group_by(MilesToCampus, Gender) %>% 
  summarise(meanprice = as.numeric(round(mean(Price), digits = 0)), 
            medianprice = as.numeric(round(median(Price), digits = 0)),  
            maxprice = as.numeric(round(max(Price), digits = 0)),  
            minprice = as.numeric(round(min(Price), digits = 0)),  
            .groups = 'drop') 
```

```{r numerical, warning=FALSE}
# Use this R-chunk to...
# ...compute and display a meaningful table of numerical summaries supporting your above graphic.

datatable(dat1, options=list(lengthMenu = c(3,10, 30)), extensions="Responsive")
```

<!-- Write a few statements here that introduce your table of numerical summaries and what they show. -->

...delete this and type here...


## Conclusion

...delete this and type an interesting final conclusion about what your graphic and numerical summaries show...



